Comparison of linear beam theories

### 2024-04-06 Appendix.tex
submition

\chapter*{MATLAB Code}
\addcontentsline{toc}{section}{MATLAB Code}
\section*{Example code for Timoshenko beam model}
\lstinputlisting{code/timoshenko_beam/TimoshenkoEig.m}

>>>>

\chapter*{MATLAB Code}
The following are the main code used in this dissertation to obtain the eigenvalues and eigenvectors of the models. The code and the dissertation is also available on GitHub at \url{https://github.com/Propagandalf-7/masters}.

The code is optimized for performance, and therefore the presentation of the code is not optimized for readability. The code is also not commented.

\addcontentsline{toc}{section}{MATLAB Code}
\section*{Example code for Timoshenko beam model}
\lstinputlisting{code/timoshenko_beam/TimoshenkoEig.m}
